---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggdollar

The goal of ggdollar is to provide a more intuitive way to set `theme()` arguments
when using the package *ggplot2*.

It's a draft, but works ok already.

## Installation

You can install the released version of ggdollar from [CRAN](https://CRAN.R-project.org) with:

``` r
remotes::install_github("moodymudskipper/ggdollar")
```

## Intro

`ggset`, `ggdo` and `ggremove` are nested lists of functions.

`ggset` lets you dig to the element you want to change,
  and apply those changes, so that `ggset$panel$background(fill = "blue")` is the same as
  `theme(panel.background = element_rec(fill = "blue"))`. The arguments are
  most of the time ultimately forwarded to an `element_*()` function and you can
  change many attributes of a component at once. `?margin` will provide the
  description of most parameters.

`ggdo` on the other hands starts from the action you want to perform, For instance
the equivalent to the above would be `ggdo$fill_background$panel("red")`.
  Typically with `ggdo` we set only a single or a couple of attributes at once.

`ggremove` is like `ggset` but helps removing components, it sets the relevant
`theme()` arguments to `element_blank()`, `NULL` or `"none"`.

For instance `ggremove$panel$background()` is the same as `theme(panel.background = element_blank())`

There would have been many other ways to organize these lists and we went for
an partially arbitrary reorganization rather than a fully systematic one.

```{r example}
library(ggdollar)
library(ggplot2) 
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) + geom_point() + 
  ggset$panel$background(fill = "white", color = "black") +
  ggdo$set_text$angle$axis$x$bottom$text(45) +
  ggremove$legend$all()
## basic example code
```


# To do : 

* support in `ggdo` attributes that aren't related to `element_*()` functions
* Play around and see what doesn't feel right
* find better names
* better doc
